---
title       : Car efficiency by weight
subtitle    : 
author      : Gorka Maiztegi
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Final project

- This is the presentation for the final project in the "Developing data products" Coursera course.
- This course is part of the "Data Science" specialization.
- The other part of the project is the Shiny app.

---

## The Dataset: _mtcars_

- According to the help file, "the data in was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models)".
- This is the summary of the dataset:

```{r, echo=FALSE}
library(datasets)
data(mtcars)
summary(mtcars)
```

---

## The regression

- We have identified a strong relationship between the weight and the efficiency.
- The image shows the linear model fitted to the data.
- Note also that there is also a relationship between the transmission type and the efficiency.

```{r, echo=FALSE}
library(ggplot2)
library(plyr)
mtcars$am <- as.factor(mtcars$am)
mtcars$am <- revalue(mtcars$am, c("0"="Automatic", "1"="Manual"))
g <- ggplot(mtcars, aes(x = wt, y = mpg, colour = am))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm", aes(colour = NA))
g <- g + labs(x = "Weight (tons)", y = "Efficiency (mpg)")
g <- g + guides(colour=guide_legend(title=NULL))
g
```

---

## The app

- A Shiny app has been created to show the previous regression, allowing to filter by transmission type.
- The app has been published to Shiny and is available in the following url: https://gmaiztegi.shinyapps.io/mtcars/
